Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-04-03 man/figures/nls_long_term_resilience.Rmd
update nls

library("mgcv")
library("rcompanion")
mg <- gam(rs~s(sev), data=d)
summary(mg)

>>>>

library("minpack.lm")
library("nls2")
library("nlshelper")
library("nlstools")

# Catalogo de funciones en Catalog of Curves for Curve Fitting
# V. Sit and M. Poulin-Costello 1994 Biometrics Information Handbook 
# https://www.for.gov.bc.ca/hfd/pubs/docs/bio/bio04.htm

set.seed(1467)
# Exponential type I

fe1 <- as.formula(rs ~ I(a*sev^b + c))
preview(fe1, data = d, start = list(a= 0.0015, b = 2, c=0.8))

e1 <- nls(fe1, data = d, start = list(a = 0.0015, b = 2, c=.8),
          trace = TRUE, control = list(maxiter = 100))
summary(e1)

set.seed(1467)

te <- nls(rs ~ I(exp(1)^(a+b*sev)), data = d, start = list(a=0.8, b = 0.03), trace = TRUE)
summary(te)

f <- as.formula(d$rs ~ d$sev + d$sev^2)
lf <- lm(f, data=d)

alpha <- 0.05
df.new <- data.frame(rs=seq(2,24, 2))
conf.dist <- predict(lf, newdata = df.new, interval="confidence", level=1-alpha) 
pred.dist <- predict(lf, newdata = df.new, interval="prediction", level=1-alpha) 
df.new[c("fit","lwr.conf", "upr.conf")] <- conf.dist
df.new[c("lwr.pred", "upr.pred")] <- pred.dist[,2:3]
p +   
  geom_ribbon(data=df.new, aes(x=rs, ymin=lwr.pred, ymax=upr.pred), alpha=0.1, inherit.aes=F, fill="blue") +
    geom_line(data=df.new, aes(x=rs, y=fit), colour="#339900", size=1)

+ 
  geom_ribbon(data=df.new, aes(x=speed, ymin=lwr.conf, ymax=upr.conf), alpha=0.2, inherit.aes=F, fill="#339900") +

p <- ggplot(d) + geom_point(aes(x=sev, y=rs))

pl <- ggplot(cars) + geom_point(aes(x=speed, y=dist), size=2, colour="#993399") + 
  xlab("Speed (mph)") + ylab("Stopping distance (ft)")

offset <- round(min(d$rs),2)

d$lrs <- log(d$rs + 0.5)
d$lsev <- log(d$sev)

l1 <- lm(d$rs~d$lsev, data=d)
plot(d$rs~d$lsev) 
abline(l1)
summary(l1)

R2 
RSSp <- sum(residuals(e1)^2)

TSS <- sum((d$rs - mean(d$rs))^2)

1 - RSSp/TSS

# R2

r2s <- function(modelo, dataframe, y){

  RSS <- sum(residuals(modelo)^2)
  TSS <- sum(dataframe[,y] - mean())

  out <- data.frame(RSS, TSS)
  return(out)

}

r2s(e1, d, "rs")

RSS

# Adjusted-R2

n <- dim(d)[1]
p <- length(coefficients(e1))

r2adj_pi <- 1 - ((n -1))/(n-p)) * (1- r2.pi)

library("mgcv")
library("rcompanion")
library("gam")

# Modelo 1 gam 
mg <- mgcv::gam(rs~s(sev), data=d, trace = TRUE)
summary(mg)
